\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[scale=0.85]{geometry}
\usepackage{lmodern}

\moderncvstyle{casual}
\definecolor{color0}{HTML}{000000}
\definecolor{color1}{HTML}{BB6588}
\definecolor{color2}{HTML}{CCAA87}
\setlength{\hintscolumnwidth}{3.5cm}

\name{Yu}{SHEN}
\extrainfo{Yu SHEN $\cdot$ Curriculum Vitae}

\begin{document}

\makecvfoot

\begin{tabular}{l r}
    \begin{minipage}{.45\textwidth}
        \fontsize{58}{58}\selectfont Yu SHEN
    \end{minipage} &
    \begin{minipage}{.55\textwidth}
        \begin{flushright}
            \normalsize \color{color1} \vspace{.3in}
            \href{mailto:shenyu.tcv@gmail.com}{\faEnvelope~shenyu.tcv@gmail.com} 
            \\
            \href{https://www.google.com/maps/place/The+Bayes+Centre,+The+University+of+Edinburgh/@55.9453104,-3.1897611,17z/data=!3m1!4b1!4m6!3m5!1s0x4887c7d062a4b737:0xe8b71b6220a53c7!8m2!3d55.9453074!4d-3.1871808!16s%2Fg%2F11gl4ml5r7?entry=ttu}{\faMapMarker~Bayes Centre (3.17), 47 Potterrow, EH8 9BT} \\
            % \href{https://dblp.org/pid/48/4462-2.html}{DBLP}~
            \href{https://github.com/InfiniteSynthesis}{\faGithub}~
            \href{https://www.linkedin.com/in/shenyutcv/}{\faLinkedin}~
            \href{https://shenyu-official.icu}{{\faCoffee} shenyu-official.icu}
             \\
            \color{color2} Last update: \today
        \end{flushright}
    \end{minipage}
\end{tabular}

\vspace{-.1in}


%---RESEARCH INTEREST SECTION--------------------------------------------------
\section{Research Interest}

\cvitem{}
{I am broadly interested in the interplay of distributed algorithms and cryptography, especially the design and analysis of blockchain protocols. My current focuses include:}
\cvlistitem{Permissionless consensus and clock synchronization.}
\cvlistitem{Blockchain transaction serialization with order fairness.}


%---EDUCATION SECTION----------------------------------------------------------
\section{Education}

\cventry{2021 -- 2025\\(expected)}
{Ph.D. in Computer Science}
{School of Informatics, University of Edinburgh}
{Scotland}
{}
{Advisor: Prof. Aggelos Kiayias and Dr. Michele Ciampi}

\cventry{2019 -- 2021}
{M.S. in Computer Science}
{Texas A\&M University}
{}
{US}
{Thesis: \href{https://oaktrust.library.tamu.edu/bitstream/handle/1969.1/195819/SHEN-THESIS-2021.pdf}{A Formal Analysis of Bitcoin Cash} \\Advisor: Prof. Juan A. Garay}

\cventry{2015 -- 2019}
{B.S. in Computer Science and Technology}
{Jilin University}
{}
{China}
{}


%---PROFESSIONAL EXPERIENCE SECTION--------------------------------------------
\section{Professional Experience}

\cventry{Aug 2022 -- Sep 2022}
{Student Engineer}
{Blockchain Technology Lab}
{}
{}
{Wrote Cardano smart contract using the Plutus platform.}

\cventry{Aug 2018 -- Aug 2019}
{Software Engineer Intern}
{Beijing ByteDance Technology Co., Ltd.}
{}
{}
{Implemented self-developed layout engine for cross-platform framework, including all flex layout properties, consistent with the latest CSS standard.}

\cventry{Oct 2017 -- Jun 2018}
{Undergraduate Research Assistant}
{Jilin University}
{}
{}
{Carried out research of Intelligent Interpretation of Genetic Data. Fixed bugs of pubMunch (medical article downloader), built an article classifier based on genotype and phenotype.}


%---PUBLICATIONS SECTION-------------------------------------------------------
\section{Publications \& Manuscripts}

\cventry{CRYPTO '24}
{\textbf{\href{https://eprint.iacr.org/2024/1296.pdf}{Universal Composable Transaction Serialization with Order Fairness}}}
{}
{}
{}
{\normalsize Michele Ciampi, Aggelos Kiayias, \underline{Yu Shen}}

\cventry{EUROCRYPT '24}
{\textbf{\href{https://eprint.iacr.org/2023/1663.pdf}{Proof-of-Work-based Consensus in Expected-Constant Time}}}
{}
{}
{}
{\normalsize Juan A. Garay, Aggelos Kiayias, \underline{Yu Shen}}

\cventry{EUROCRYPT '24}
{\textbf{\href{https://eprint.iacr.org/2023/1253.pdf}{Ordering Transactions with Bounded Unfairness: Definitions, Complexity and Constructions}}}
{}
{}
{}
{\normalsize Aggelos Kiayias, Nikos Leonardos, \underline{Yu Shen}}

\cventry{TCC '22}
{\textbf{\href{https://eprint.iacr.org/2022/1220.pdf}{Permissionless Clock Synchronization with Public Setup}}}
{}
{}
{}
{\normalsize Juan A. Garay, Aggelos Kiayias, \underline{Yu Shen}}

\cventry{ACM AFT '21}
{\textbf{\href{https://eprint.iacr.org/2021/143.pdf}{On Bitcoin Cash's Target Recalculation Functions}}}
{}
{}
{}
{\normalsize Juan A. Garay, \underline{Yu Shen}}

%---ACADEMIC SERVICE SECTION---------------------------------------------------
\section{Academic Service}

\cvitem{Subreviewer}{CiC '24, SCN '24, CANS '24, CRYPTO '24, EUROCRYPT '24, AFT'23, MARBLE '23, DAPPS '23, Asiacrypt '22, Indocrypt '22, IEEE TDSC '22}

%---TEACHING ASSISTANT SECTION-------------------------------------------------
\section{Teaching Assistant}

\cventry{Fall 2022, 2023, 2024}
{Blockchain and Distributed Ledger}
{}
{}
{}
{INFR11238 / INFR11144, University of Edinburgh}

\cventry{Spring 2022, 2023}
{Introduction to Modern Cryptography}
{}
{}
{}
{INFR11131, University of Edinburgh}

\cventry{Spring 2021}
{Design and Analysis of Algorithms}
{}
{}
{}
{CSCE411, Texas A\&M University}

\cventry{Fall 2020}
{Foundations of Blockchains}
{}
{}
{}
{CSCE489 / CSCE689, Texas A\&M University
    %Graded assignments and gave lectures about Proof-of-Stake in CSCE689: Foundations and Applications of Blockchains, Fall 2020.
}

%---ACADEMIC SERVICE SECTION---------------------------------------------------
\section{Invited Talks}

\cventry{CIBE '24}
{\href{https://cibe24.bici.events/home}{Parallel Blockchains and Applications}}
{}
{}
{}
{\normalsize Juan A. Garay, Aggelos Kiayias, \underline{Yu Shen}}

\cventry{EUROCRYPT '24}
{\href{https://youtu.be/uvAEvkGZymg?t=2400}{Proof-of-Work-based Consensus in Expected-Constant Time}}
{}
{}
{}
{\normalsize Juan A. Garay, Aggelos Kiayias, \underline{Yu Shen}}

\cventry{EUROCRYPT '24}
{\href{https://youtu.be/uvAEvkGZymg}{Ordering Transactions with Bounded Unfairness: Definitions, Complexity and Constructions}}
{}
{}
{}
{\normalsize Aggelos Kiayias, Nikos Leonardos, \underline{Yu Shen}}

\cventry{Texas Crypto Day '23}
{\href{https://texascryptoday.github.io/events/2-UTAustin.html}{Permissionless Clock Synchronization with Public Setup}}
{}
{}
{}
{\normalsize Juan A. Garay, Aggelos Kiayias, \underline{Yu Shen}}

\cventry{TCC '22}
{\href{https://youtu.be/JUYzY-1mcYM}{Permissionless Clock Synchronization with Public Setup}}
{}
{}
{}
{\normalsize Juan A. Garay, Aggelos Kiayias, \underline{Yu Shen}}

\cventry{ACM AFT '21}
{{\href{https://youtu.be/5K6HNCtLPtk}{On Bitcoin Cash's Target Recalculation Functions}}}
{}
{}
{}
{\normalsize Juan A. Garay, \underline{Yu Shen}}

%---OPEN SOURCE CONTRIBUTIONS SECTION------------------------------------------
\section{Open Source Contributions}

\cvitem{Chromium}
{Bug-fix in layout engine. Solved inconsistency between latest CSS standard and the actual layout result. Solved error in chromum fast web test. Commit merged in Chromium Version 73.}

\cvitem{Web Platform Test}
{Added new test case page and reference for grid-auto-repeat multiple values.}


%---SKILLS SECTION-------------------------------------------------------------
\section{Skills}

\cvitem{Languages}
{Mandarin, English}
\cvitem{Prog. Language}
{C/C++, TypeScript, Python, Java, Objective-C}
\cvitem{Other}
{git, vim, \LaTeX,WebDev (HTML5, CSS3, Node.js, React, Flask), REST}


%---REFERENCE SECTION----------------------------------------------------------
\section{References}

\cvitem{}{References available upon request.}

\end{document}